# chapter15: Getting Your Data into Shape
```{r}
library(gcookbook) # For the data set
head(heightweight)

str(heightweight)
```
## 15.1.Creating a Data Frame
```{r}
# Two starting vectors
g <- c("A", "B", "C")
x <- 1:3

dat <- data.frame(g, x)
dat
```
## 15.2.Getting Information About a Data Structture    
```{r}
lst <- list(group = g, value = x)    # A list of vectors

dat <- as.data.frame(lst)
    
str(ToothGrowth)

tg <- ToothGrowth
tg$supp <- as.character(tg$supp)

str(tg)

# Print out the columns by themselves

# From old data frame (factor)
ToothGrowth$supp

# From new data frame (character)
tg$supp
```
## 15.3.Adding a Column to a Data Frame
```{r}
#data$newcol <- NA
dat$newcol <- NA
    
#data$newcol <- vec
dat$newcol <- vec
```
## 15.4.Deleting a Column from a Data Frame
```{r}
data$badcol <- NULL
    
# Return data without badcol
data <- subset(data, select = -badcol)

# Exclude badcol and othercol
data <- subset(data, select = c(-badcol, -othercol))
```
## 15.5.Renaming Columns in a Data Frame
```{r}
names(dat) <- c("name1", "name2", "name3")
    
library(gcookbook) # For the data set
names(anthoming)   # Print the names of the columns

names(anthoming)[names(anthoming) == "ctrl"] <- c("Control")
names(anthoming)[names(anthoming) == "expt"] <- c("Experimental")
names(anthoming)
    
names(anthoming)[1] <- "Angle"
names(anthoming)
```
## 15.6.Reordering Columns in a Data Frame
```{r}
dat <- dat[c(1,3,2)]
    
dat <- dat[c("col1", "col3", "col2")]
    
library(gcookbook) # For the data set
anthoming

anthoming[c(1,3,2)]     # List-style indexing

# Putting nothing before the comma means to select all rows
anthoming[, c(1,3,2)]   # Matrix-style indexing

anthoming[3]     # List-style indexing

anthoming[, 3]   # Matrix-style indexing

anthoming[, 3, drop=FALSE]   # Matrix-style indexing with drop=FALSE
```
## 15.7.Getting a Subset of a Data Frame
```{r}
library(gcookbook) # For the data set
head(climate)
    
head(subset(climate, Source == "Berkeley", select = c(Year, Anomaly10y)))

head(subset(climate, Source == "Berkeley"  &  Year >= 1900  &  Year <= 2000,
       select = c(Year, Anomaly10y)))

head(climate[climate$Source=="Berkeley" & climate$Year >= 1900 & climate$Year <= 2000,
        c("Year", "Anomaly10y")])
    
    
head(climate[climate$Source=="Berkeley" & climate$Year >= 1900 & climate$Year <= 2000,
        c("Year", "Anomaly10y"), drop=FALSE])
    
    
head(climate[1:100, c(2, 5)])
```    
## 15.8.Changing the Order of Factor Levels  
```{r}
# By default, levels are ordered alphabetically
sizes <- factor(c("small", "large", "large", "small", "medium"))
sizes

# Change the order of levels
sizes <- factor(sizes, levels = c("small", "medium", "large"))
sizes

factor(sizes, levels = rev(levels(sizes)))
```
## 15.9.Changing the Order of Factor Levels Based on Data Values
```{r}
# Make a copy since we'll modify it
iss <- InsectSprays
iss$spray

iss$spray <- reorder(iss$spray, iss$count, FUN=mean)
iss$spray

attr(,"scores")
```
## 15.10.Changing the Names of Factor Levels
```{r}
sizes <- factor(c( "small", "large", "large", "small", "medium"))
sizes

levels(sizes)

# With revalue(), pass it a named vector with the mappings
sizes1 <- revalue(sizes, c(small="S", medium="M", large="L"))
sizes1

# Can also use quotes -- useful if there are spaces or other strange characters
revalue(sizes, c("small"="S", "medium"="M", "large"="L"))

# mapvalues() lets you use two separate vectors instead of a named vector
mapvalues(sizes, c("small", "medium", "large"), c("S", "M", "L"))

sizes <- factor(c( "small", "large", "large", "small", "medium"))

# Index into the levels and rename each one
levels(sizes)[levels(sizes)=="large"]  <- "L"
levels(sizes)[levels(sizes)=="medium"] <- "M"
levels(sizes)[levels(sizes)=="small"]  <- "S"
sizes

sizes <- factor(c("small", "large", "large", "small", "medium"))
levels(sizes) <- list(S="small", M="medium", L="large")
sizes

# By default, levels are ordered alphabetically
sizes <- factor(c("small", "large", "large", "small", "medium"))

levels(sizes)[1] <- "L"
sizes

# Rename all levels at once
levels(sizes) <- c("L", "M", "S")
sizes
```
## 15.11.Removing Unused Levels from a Factor 
```{r}
sizes <- factor(c("small", "large", "large", "small", "medium"))
sizes <- sizes[1:3]
sizes

sizes <- droplevels(sizes)
sizes
```
## 15.12.Changing the Names of Items in a Character Vector 
```{r}
sizes <- c("small", "large", "large", "small", "medium")
sizes

# With revalue(), pass it a named vector with the mappings
sizes1 <- revalue(sizes, c(small="S", medium="M", large="L"))
sizes1

# Can also use quotes -- useful if there are spaces or other strange characters
revalue(sizes, c("small"="S", "medium"="M", "large"="L"))

# mapvalues() lets you use two separate vectors instead of a named vector
mapvalues(sizes, c("small", "medium", "large"), c("S", "M", "L"))

sizes <- c("small", "large", "large", "small", "medium")
sizes

sizes[sizes=="small"]  <- "S"
sizes[sizes=="medium"] <- "M"
sizes[sizes=="large"]  <- "L"

sizes
```
## 15.13.Recoding a Categorical Variable to Another Categorical Variable
```{r}
# Work on a subset of the PlantGrowth data set
pg <- PlantGrowth[c(1,2,11,21,22), ]
pg

pg <- PlantGrowth

oldvals <- c("ctrl", "trt1", "trt2")
newvals <- factor(c("No",   "Yes",  "Yes"))

pg$treatment <- newvals[ match(pg$group, oldvals) ]
    
pg$treatment[pg$group == "ctrl"] <- "no"
pg$treatment[pg$group == "trt1"] <- "yes"
pg$treatment[pg$group == "trt2"] <- "yes"

# Convert to a factor
pg$treatment <- factor(pg$treatment)
pg

pg$newcol[pg$group == "ctrl"  &  pg$weight <  5] <- "no_small"
pg$newcol[pg$group == "ctrl"  &  pg$weight >= 5] <- "no_large"
pg$newcol[pg$group == "trt1"] <- "yes"
pg$newcol[pg$group == "trt2"] <- "yes"

pg$newcol <- factor(pg$newcol)
pg

pg$weighttrt <- interaction(pg$weightcat, pg$treatment)
pg
```
## 15.14.Recoding a Continuous Variable to a Categorical Variable
```{r}
# Work on a subset of the PlantGrowth data set
pg <- PlantGrowth[c(1,2,11,21,22), ]
pg

pg$wtclass <- cut(pg$weight, breaks = c(0, 5, 6, Inf))
pg

pg$wtclass <- cut(pg$weight, breaks = c(0, 5, 6, Inf),
                  labels = c("small", "medium", "large"))
pg

cut(pg$weight, breaks = c(0, 5, 6, Inf), right = FALSE)
```
## 15.15.Transforming Variables
```{r}
library(gcookbook) # For the data set
# Make a copy of the data
hw <- heightweight
head(hw)

hw$heightCm <- hw$heightIn * 2.54
head(hw)

hw <- transform(hw, heightCm = heightIn * 2.54, weightKg = weightLb / 2.204)
library(plyr)
hw <- mutate(hw, heightCm = heightIn * 2.54, weightKg = weightLb / 2.204)
head(hw)

# These all have the same effect:
hw <- transform(hw, bmi = weightKg / (heightCm / 100)^2)
hw <- mutate(hw, bmi = weightKg / (heightCm / 100)^2)
hw$bmi <- hw$weightKg / (hw$heightCm/100)^2
head(hw)

hw <- heightweight
hw <- mutate(hw,
    heightCm = heightIn * 2.54,
    weightKg = weightLb / 2.204,
    bmi = weightKg / (heightCm / 100)^2)
```   
## 15.16.Transforming variables by Group
```{r}
library(MASS) # For the data set
library(plyr)
cb <- ddply(cabbages, "Cult", transform, DevWt = HeadWt - mean(HeadWt))

cabbages

transform(cabbages, DevWt = HeadWt - mean(HeadWt))

library(plyr)
cb <- ddply(cabbages, "Cult", transform, DevWt = HeadWt - mean(HeadWt))
cb

# The data before normalizing
ggplot(cb, aes(x=Cult, y=HeadWt)) + geom_boxplot()

# After normalizing
ggplot(cb, aes(x=Cult, y=DevWt)) + geom_boxplot()
    
    
ddply(cabbages, c("Cult", "Date"), transform,
      DevWt = HeadWt - mean(HeadWt), DevVitC = VitC - mean(VitC))
```
## 15.17.Summarizing Data by Groups
```{r}
library(MASS) # For the data set
library(plyr)

ddply(cabbages, c("Cult", "Date"), summarise, Weight = mean(HeadWt), 
      VitC = mean(VitC))

head(cabbages)

library(plyr)
summarise(cabbages, Weight = mean(HeadWt))

library(plyr)
ddply(cabbages, "Cult", summarise, Weight = mean(HeadWt))

ddply(cabbages, c("Cult", "Date"), summarise, Weight = mean(HeadWt), 
      VitC = mean(VitC))

ddply(cabbages, c("Cult", "Date"), summarise,
      Weight = mean(HeadWt),
      sd = sd(HeadWt),
      n = length(HeadWt))

c1 <- cabbages                # Make a copy
c1$HeadWt[c(1,20,45)] <- NA   # Set some values to NA

ddply(c1, c("Cult", "Date"), summarise,
      Weight = mean(HeadWt),
      sd = sd(HeadWt),
      n = length(HeadWt))

ddply(c1, c("Cult", "Date"), summarise,
      Weight = mean(HeadWt, na.rm=TRUE),
      sd = sd(HeadWt, na.rm=TRUE),
      n = sum(!is.na(HeadWt)))

# Copy cabbages and remove all rows with both c52 and d21
c2 <- subset(c1, !( Cult=="c52" & Date=="d21" ) )

c2a <- ddply(c2, c("Cult", "Date"), summarise,
      Weight = mean(HeadWt, na.rm=TRUE),
      sd = sd(HeadWt, na.rm=TRUE),
      n = sum(!is.na(HeadWt)))
c2a

# Make the graph
ggplot(c2a, aes(x=Date, fill=Cult, y=Weight)) + geom_bar(position="dodge")

    
c2b <- ddply(c2, c("Cult", "Date"), .drop=FALSE, summarise,
      Weight = mean(HeadWt, na.rm=TRUE),
      sd = sd(HeadWt, na.rm=TRUE),
      n = sum(!is.na(HeadWt)))
c2b

# Make the graph
ggplot(c2b, aes(x=Date, fill=Cult, y=Weight)) + geom_bar(position="dodge")
```
## 15.18.Summarizing Data with Standard Errors and Confidence Intervals
```{r}
library(MASS) # For the data set
library(plyr)

ca <- ddply(cabbages, c("Cult", "Date"), summarise,
      Weight = mean(HeadWt, na.rm=TRUE),
      sd = sd(HeadWt, na.rm=TRUE),
      n = sum(!is.na(HeadWt)),
      se = sd/sqrt(n))

ca

ddply(cabbages, c("Cult", "Date"), summarise,
      Weight = mean(HeadWt, na.rm=TRUE),
      sd = sd(HeadWt, na.rm=TRUE),
      n = sum(!is.na(HeadWt)),
      se = sd / sqrt(n))
    
    
ciMult <- qt(.975, ca$n-1)
ciMult

ca$ci <- ca$se * ciMult

ca$ci95 <- ca$se * qt(.975, ca$n)
    
    
summarySE <- function(data=NULL, measurevar, groupvars=NULL,
                      conf.interval=.95, na.rm=FALSE, .drop=TRUE) {
    require(plyr)

    # New version of length that can handle NAs: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary
    datac <- ddply(data, groupvars, .drop=.drop,
                   .fun = function(xx, col, na.rm) {
                           c( n    = length2(xx[,col], na.rm=na.rm),
                              mean = mean   (xx[,col], na.rm=na.rm),
                              sd   = sd     (xx[,col], na.rm=na.rm)
                              )
                          },
                    measurevar,
                    na.rm
             )

    # Rename the "mean" column
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$n)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval:
    # e.g., if conf.interval is .95, use .975 (above/below), and use
    #  df=n-1, or if n==0, use df=0
    ciMult <- qt(conf.interval/2 + .5, datac$n-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
    
# Remove all rows with both c52 and d21
c2 <- subset(cabbages, !( Cult=="c52" & Date=="d21" ) )

# Set some values to NA
c2$HeadWt[c(1,20,45)] <- NA


summarySE(c2, "HeadWt", c("Cult", "Date"), conf.interval=.99,
          na.rm=TRUE, .drop=FALSE)
```
## 15.19.Converting Data from Wide to Long
```{r}
library(gcookbook) # For the data set
anthoming

library(reshape2)
melt(anthoming, id.vars="angle", variable.name="condition", value.name="count")

drunk

melt(drunk, id.vars="sex", measure.vars=c("0-29", "30-39"),
     variable.name="age", value.name="count")

plum_wide

melt(plum_wide, id.vars=c("length","time"), variable.name="survival", 
                           value.name="count")

# Make a copy of the data
co <- corneas
co

# Add an ID column
co$id <- 1:nrow(co)

melt(co, id.vars="id", variable.name="eye", value.name="thickness")
```
## 15.20.Converting Data from Long to Wide
```{r}
library(gcookbook) # For the data set
plum

library(reshape2)
dcast(plum, length + time ~ survival, value.var="count")

dcast(plum, time ~ length + survival, value.var="count")
```
## 15.21.Converting a Time Series Object to Times
```{r}
# Look at nhtemp Time Series object
nhtemp

# Get times for each observation
as.numeric(time(nhtemp))

# Get value of each observation
as.numeric(nhtemp)

# Put them in a data frame
nht <- data.frame(year=as.numeric(time(nhtemp)), temp=as.numeric(nhtemp))
head(nht)

head(presidents)

pres_rating <- data.frame(
    year    = as.numeric(time(presidents)),
    rating  = as.numeric(presidents)
)
head(pres_rating)

pres_rating2 <- data.frame(
    year    = as.numeric(floor(time(presidents))),
    quarter = as.numeric(cycle(presidents)),
    rating  = as.numeric(presidents)
)
head(pres_rating2)
```