# chapter: Scatter Plots
## 5.1.Making a Basic scatter Plot
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set
library(ggplot2)

# List the two columns we'll use
head(heightweight[, c("ageYear", "heightIn")])


    
ggplot(heightweight, aes(x=ageYear, y=heightIn)) + geom_point()
    
    
ggplot(heightweight, aes(x=ageYear, y=heightIn)) + geom_point(shape=21)
    
    
ggplot(heightweight, aes(x=ageYear, y=heightIn)) + geom_point(size=1.5)
```
## 5.2.Grouping Data Points by a Variable Using  
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set
# Show the three columns we'll use
head(heightweight[, c("sex", "ageYear", "heightIn")])

ggplot(heightweight, aes(x=ageYear, y=heightIn, colour=sex)) + geom_point()

ggplot(heightweight, aes(x=ageYear, y=heightIn, shape=sex)) + geom_point()
    
    
ggplot(heightweight, aes(x=ageYear, y=heightIn, shape=sex, colour=sex)) +
    geom_point()
    
    
ggplot(heightweight, aes(x=ageYear, y=heightIn, shape=sex, colour=sex)) +
    geom_point() +
    scale_shape_manual(values=c(1,2)) +
    scale_colour_brewer(palette="Set1")
    
```  
## 5.3.Using Different Point Shapes
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set

ggplot(heightweight, aes(x=ageYear, y=heightIn)) + geom_point(shape=3)
    
    
# Use slightly larger points and use a shape scale with custom values
ggplot(heightweight, aes(x=ageYear, y=heightIn, shape=sex)) +
    geom_point(size=3) + scale_shape_manual(values=c(1, 4))
    
    
# Make a copy of the data
hw <- heightweight
# Categorize into <100 and >=100 groups
hw$weightGroup <- cut(hw$weightLb, breaks=c(-Inf, 100, Inf),
                      labels=c("< 100", ">= 100"))

# Use shapes with fill and color, and use colors that are empty (NA) and 
# filled
ggplot(hw, aes(x=ageYear, y=heightIn, shape=sex, fill=weightGroup)) +
    geom_point(size=2.5) +
    scale_shape_manual(values=c(21, 24)) +
    scale_fill_manual(values=c(NA, "black"),
      guide=guide_legend(override.aes=list(shape=21)))
```    
## 5.4.Mapping a Continuous Variable to Color or Size
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set

# List the four columns we'll use
head(heightweight[, c("sex", "ageYear", "heightIn", "weightLb")])

ggplot(heightweight, aes(x=ageYear, y=heightIn, colour=weightLb)) + geom_point()

ggplot(heightweight, aes(x=ageYear, y=heightIn, size=weightLb)) + geom_point()
    
    
ggplot(heightweight, aes(x=weightLb, y=heightIn, fill=ageYear)) +
    geom_point(shape=21, size=2.5) +
    scale_fill_gradient(low="black", high="white")

# Using guide_legend() will result in a discrete legend instead of a colorbar
ggplot(heightweight, aes(x=weightLb, y=heightIn, fill=ageYear)) +
    geom_point(shape=21, size=2.5) +
    scale_fill_gradient(low="black", high="white", breaks=12:17,
                        guide=guide_legend())
    
    
ggplot(heightweight, aes(x=ageYear, y=heightIn, size=weightLb, colour=sex)) +
    geom_point(alpha=.5) +
    scale_size_area() +     # Make area proportional to numeric value
    scale_colour_brewer(palette="Set1")
```    
## 5.5.Dealing with Overplotting
```{r,fig.width=6,fig.height=5}
sp <- ggplot(diamonds, aes(x=carat, y=price))

sp + geom_point()
sp + geom_point(alpha=.1)

sp + geom_point(alpha=.01)
    
    
sp + stat_bin2d()

sp + stat_bin2d(bins=50) +
    scale_fill_gradient(low="lightblue", high="red", limits=c(0, 6000))
    
    
#install.packages("hexbin")
library(hexbin)

sp + stat_binhex() +
    scale_fill_gradient(low="lightblue", high="red",
                        limits=c(0, 8000))

sp + stat_binhex() +
    scale_fill_gradient(low="lightblue", high="red",
                        breaks=c(0, 250, 500, 1000, 2000, 4000, 6000),
                        limits=c(0, 6000))
    
    
sp1 <- ggplot(ChickWeight, aes(x=Time, y=weight))

sp1 + geom_point()

sp1 + geom_point(position="jitter")
# Could also use geom_jitter(), which is equivalent

sp1 + geom_point(position=position_jitter(width=.5, height=0))
    
    
sp1 + geom_boxplot(aes(group=Time))
    
```    
## 5.6.Adding Fitted Regression Model Lines
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set

# The base plot
sp <- ggplot(heightweight, aes(x=ageYear, y=heightIn))

sp + geom_point() + stat_smooth(method=lm)
    
    
# 99% confidence region
sp + geom_point() + stat_smooth(method=lm, level=0.99)

# No confidence region
sp + geom_point() + stat_smooth(method=lm, se=FALSE)
    
    
sp + geom_point(colour="grey60") +
    stat_smooth(method=lm, se=FALSE, colour="black")
    
    
sp + geom_point(colour="grey60") + stat_smooth()
sp + geom_point(colour="grey60") + stat_smooth(method=loess)
    
    
library(MASS) # For the data set

b <- biopsy

b$classn[b$class=="benign"]    <- 0
b$classn[b$class=="malignant"] <- 1

head(b)

ggplot(b, aes(x=V1, y=classn)) +
    geom_point(position=position_jitter(width=0.3, height=0.06), alpha=0.4,
               shape=21, size=1.5) +
    stat_smooth(method=glm, family=binomial)
    
    
sps <- ggplot(heightweight, aes(x=ageYear, y=heightIn, colour=sex)) +
       geom_point() +
       scale_colour_brewer(palette="Set1")

sps + geom_smooth()
    
    
sps + geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
    
```
## 5.7.Adding Fitted Lines from an Existing Model
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set

model <- lm(heightIn ~ ageYear + I(ageYear^2), heightweight)
model


# Create a data frame with ageYear column, interpolating across range
xmin <- min(heightweight$ageYear)
xmax <- max(heightweight$ageYear)
predicted <- data.frame(ageYear=seq(xmin, xmax, length.out=100))

# Calculate predicted values of heightIn
predicted$heightIn <- predict(model, predicted)
head(predicted)

sp <- ggplot(heightweight, aes(x=ageYear, y=heightIn)) +
      geom_point(colour="grey40")

sp + geom_line(data=predicted, size=1)
    
    
# Given a model, predict values of yvar from xvar
# This supports one predictor and one predicted variable
# xrange: If NULL, determine the x range from the model object. If a vector with
#   two numbers, use those as the min and max of the prediction range.
# samples: Number of samples across the x range.
# ...: Further arguments to be passed to predict()
predictvals <- function(model, xvar, yvar, xrange=NULL, samples=100, ...) {

  # If xrange isn't passed in, determine xrange from the models.
  # Different ways of extracting the x range, depending on model type
  if (is.null(xrange)) {
    if (any(class(model) %in% c("lm", "glm")))
      xrange <- range(model$model[[xvar]])
    else if (any(class(model) %in% "loess"))
      xrange <- range(model$x)
  }

  newdata <- data.frame(x = seq(xrange[1], xrange[2], length.out = samples))
  names(newdata) <- xvar
  newdata[[yvar]] <- predict(model, newdata = newdata, ...)
  newdata
}
    
    
modlinear <- lm(heightIn ~ ageYear, heightweight)

modloess  <- loess(heightIn ~ ageYear, heightweight)
    
    
lm_predicted    <- predictvals(modlinear, "ageYear", "heightIn")
loess_predicted <- predictvals(modloess, "ageYear", "heightIn")

sp + geom_line(data=lm_predicted, colour="red", size=.8) +
     geom_line(data=loess_predicted, colour="blue", size=.8)
    
    
library(MASS) # For the data set
b <- biopsy

b$classn[b$class=="benign"]    <- 0
b$classn[b$class=="malignant"] <- 1
    
    
fitlogistic <- glm(classn ~ V1, b, family=binomial)
    
    
# Get predicted values
glm_predicted <- predictvals(fitlogistic, "V1", "classn", type="response")

ggplot(b, aes(x=V1, y=classn)) +
    geom_point(position=position_jitter(width=.3, height=.08), alpha=0.4,
               shape=21, size=1.5) +
    geom_line(data=glm_predicted, colour="#1177FF", size=1)
    
```
## 5.8.Adding Fitted Lines from Multiple Existing Models
```{r,fig.width=6,fig.height=5}
make_model <- function(data) {
    lm(heightIn ~ ageYear, data)
}
    
    
library(gcookbook) # For the data set
library(plyr)
models <- dlply(heightweight, "sex", .fun = make_model)

# Print out the list of two lm objects, f and m
models

predvals <- ldply(models, .fun=predictvals, xvar="ageYear", yvar="heightIn")
head(predvals)

    
ggplot(heightweight, aes(x=ageYear, y=heightIn, colour=sex)) +
    geom_point() + geom_line(data=predvals)
    
    
predvals <- ldply(models, .fun=predictvals, xvar="ageYear", yvar="heightIn",
                   xrange=range(heightweight$ageYear))
    
    
ggplot(heightweight, aes(x=ageYear, y=heightIn, colour=sex)) +
    geom_point() + geom_line(data=predvals)
    
```
## 5.9.Adding Annotations with Model Coefficients
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set

model <- lm(heightIn ~ ageYear, heightweight)
summary(model)

# First generate prediction data
pred <- predictvals(model, "ageYear", "heightIn")
sp <- ggplot(heightweight, aes(x=ageYear, y=heightIn)) + geom_point() +
    geom_line(data=pred)

sp + annotate("text", label="r^2=0.42", x=16.5, y=52)
    
    
sp + annotate("text", label="r^2 == 0.42", parse = TRUE, x=16.5, y=52)
    
    
expression(r^2 == 0.42)  # Valid

expression(r^2 == 0.42)


expression(r^2 == 0.42)   # Not valid
    
eqn <- as.character(as.expression(
  substitute(italic(y) == a + b * italic(x) * "," ~~ italic(r)^2 ~ "=" ~ r2,
    list(a = format(coef(model)[1], digits=3),
         b = format(coef(model)[2], digits=3),
         r2 = format(summary(model)$r.squared, digits=2)
        ))))
eqn

#"italic(y) == \"37.4\" + \"1.75\" * italic(x) * \",\" ~ ~italic(r)^2 ~ \"=\" ~ 
#\"0.42\""


parse(text=eqn)  # Parsing turns it into an expression

expression(italic(y) == "37.4" + "1.75" * italic(x) * "," ~ ~italic(r)^2 ~ "=" ~ 
"0.42")
    
    
sp + annotate("text", label=eqn, parse=TRUE, x=Inf, y=-Inf, hjust=1.1, vjust=-.5)
    
    
ggplot(faithful, aes(x=eruptions, y=waiting)) + geom_point() + geom_rug()
    
    
ggplot(faithful, aes(x=eruptions, y=waiting)) + geom_point() +
    geom_rug(position="jitter", size=.2)
    
```
## 5.11.Labeling Points in a Scatter Plot
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set
subset(countries, Year==2009 & healthexp>2000)

sp <- ggplot(subset(countries, Year==2009 & healthexp>2000),
             aes(x=healthexp, y=infmortality)) +
      geom_point()

sp + annotate("text", x=4350, y=5.4, label="Canada") +
     annotate("text", x=7400, y=6.8, label="USA")
    
    
sp + geom_text(aes(label=Name), size=4)
    
    
sp + geom_text(aes(label=Name), size=4, vjust=0)

# Add a little extra to y
sp + geom_text(aes(y=infmortality+.1, label=Name), size=4, vjust=0)
    
    
sp + geom_text(aes(label=Name), size=4, hjust=0)

sp + geom_text(aes(x=healthexp+100, label=Name), size=4, hjust=0)
    
    
cdat <- subset(countries, Year==2009 & healthexp>2000)

cdat$Name1 <- cdat$Name
    
    
idx <- cdat$Name1 %in% c("Canada", "Ireland", "United Kingdom", "United States",
                         "New Zealand", "Iceland", "Japan", "Luxembourg",
                         "Netherlands", "Switzerland")
idx


cdat$Name1[!idx] <- NA
    
    
cdat

    
    
ggplot(cdat, aes(x=healthexp, y=infmortality)) +
    geom_point() +
    geom_text(aes(x=healthexp+100, label=Name1), size=4, hjust=0) +
    xlim(2000, 10000)
```
## 5.12.Creating a Balloon Plot
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set

cdat <- subset(countries, Year==2009 &
    Name %in% c("Canada", "Ireland", "United Kingdom", "United States",
                "New Zealand", "Iceland", "Japan", "Luxembourg",
                "Netherlands", "Switzerland"))

cdat

    
    
p <- ggplot(cdat, aes(x=healthexp, y=infmortality, size=GDP)) +
     geom_point(shape=21, colour="black", fill="cornsilk")

# GDP mapped to radius (default with scale_size_continuous)
p

# GDP mapped to area instead, and larger circles
p + scale_size_area(max_size=15)
    
    
# Add up counts for male and female
hec <- HairEyeColor[,,"Male"] + HairEyeColor[,,"Female"]

# Convert to long format
library(reshape2)
hec <- melt(hec, value.name="count")

ggplot(hec, aes(x=Eye, y=Hair)) +
    geom_point(aes(size=count), shape=21, colour="black", fill="cornsilk") +
    scale_size_area(max_size=20, guide=FALSE) +
    geom_text(aes(y=as.numeric(Hair)-sqrt(count)/22, label=count), vjust=1,
              colour="grey60", size=4)
    
```
## 5.13.Making a Scatter Plot Matrix
```{r,fig.width=6,fig.height=5}
library(gcookbook) # For the data set
c2009 <- subset(countries, Year==2009,
                select=c(Name, GDP, laborrate, healthexp, infmortality))

head(c2009)

pairs(c2009[,2:5])
    
    
panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...) {
    usr <- par("usr")
    on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y, use="complete.obs"))
    txt <- format(c(r, 0.123456789), digits=digits)[1]
    txt <- paste(prefix, txt, sep="")
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex =  cex.cor * (1 + r) / 2)
}
    
    
panel.hist <- function(x, ...) {
    usr <- par("usr")
    on.exit(par(usr))
    par(usr = c(usr[1:2], 0, 1.5) )
    h <- hist(x, plot = FALSE)
    breaks <- h$breaks
    nB <- length(breaks)
    y <- h$counts
    y <- y/max(y)
    rect(breaks[-nB], 0, breaks[-1], y, col="white", ...)
}
    
    
pairs(c2009[,2:5], upper.panel = panel.cor,
                   diag.panel  = panel.hist,
                   lower.panel = panel.smooth)
    
    
panel.lm <- function (x, y, col = par("col"), bg = NA, pch = par("pch"),
                            cex = 1, col.smooth = "black", ...) {
    points(x, y, pch = pch, col = col, bg = bg, cex = cex)
    abline(stats::lm(y ~ x),  col = col.smooth, ...)
}
    
    
pairs(c2009[,2:5], pch=".",
                   upper.panel = panel.cor,
                   diag.panel  = panel.hist,
                   lower.panel = panel.lm)
```
