# chapter13: Miscellaneous Graphs
## 13.1.Making a Correlation Matrix
```{r,fig.width=7,fig.height=5}
library(ggplot2)
head(mtcars)

mcor <- cor(mtcars)

# Print mcor and round to 2 digits
round(mcor, digits=2)

#install.packages("corrplot")
library(corrplot)

corrplot(mcor)
    
corrplot(mcor, method="shade", shade.col=NA, tl.col="black", tl.srt=45)
    
    
# Generate a lighter palette
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))

corrplot(mcor, method="shade", shade.col=NA, tl.col="black", tl.srt=45,
         col=col(200), addCoef.col="black", addcolorlabel="no", order="AOE")
```    
## 13.2.Plotting a Functioon
```{r,fig.width=7,fig.height=5}
# The data frame is only used for setting the range
p <- ggplot(data.frame(x=c(-3,3)), aes(x=x))

p + stat_function(fun = dnorm)
    
p + stat_function(fun=dt, args=list(df=2))
    
myfun <- function(xvar) {
    1/(1 + exp(-xvar + 10))
}

ggplot(data.frame(x=c(0, 20)), aes(x=x)) + stat_function(fun=myfun)
```  
## 13.3.Shading a Subregion Under a Function Curve
```{r,fig.width=7,fig.height=5}
# Return dnorm(x) for 0 < x < 2, and NA for all other x
dnorm_limit <- function(x) {
    y <- dnorm(x)
    y[x < 0  |  x > 2] <- NA
    return(y)
}

# ggplot() with dummy data
p <- ggplot(data.frame(x=c(-3, 3)), aes(x=x))

p + stat_function(fun=dnorm_limit, geom="area", fill="blue", alpha=0.2) +
    stat_function(fun=dnorm)
    
limitRange <- function(fun, min, max) {
    function(x) {
        y <- fun(x)
        y[x < min  |  x > max] <- NA
        return(y)
    }
}
    
# This returns a function
dlimit <- limitRange(dnorm, 0, 2)

# Now we'll try out the new function -- it only returns values for inputs
# between 0 and 2
dlimit(-2:4)

p + stat_function(fun = dnorm) +
    stat_function(fun = limitRange(dnorm, 0, 2),
                  geom="area", fill="blue", alpha=0.2)
```    
## 13.4.Creating a Network Graph  
```{r,fig.width=7,fig.height=5}
# May need to install first, with install.packages("igraph")
#install.packages("igraph")
library(igraph)

# Specify edges for a directed graph
gd <- graph(c(1,2, 2,3, 2,4, 1,4, 5,5, 3,6))
plot(gd)

# For an undirected graph
gu <- graph(c(1,2, 2,3, 2,4, 1,4, 5,5, 3,6), directed=FALSE)
# No labels
plot(gu, vertex.label=NA)
    
str(gd)

str(gu)

set.seed(229)
plot(gu)
    
library(gcookbook) # For the data set
head(madmen2)

# Create a graph object from the data set
g <- graph.data.frame(madmen2, directed=TRUE)

# Remove unnecessary margins
par(mar=c(0,0,0,0))

plot(g, layout=layout.fruchterman.reingold, vertex.size=8, edge.arrow.size=0.5,
     vertex.label=NA)

g <- graph.data.frame(madmen, directed=FALSE)
par(mar=c(0,0,0,0))  # Remove unnecessary margins
plot(g, layout=layout.circle, vertex.size=8, vertex.label=NA)
```    
## 13.5.Using Text Labels in a Network Graph    
```{r,fig.width=7,fig.height=5}
library(igraph)
library(gcookbook) # For the data set
# Copy madmen and drop every other row
m <- madmen[1:nrow(madmen) %% 2 == 1, ]
g <- graph.data.frame(m, directed=FALSE)

# Print out the names of each vertex
V(g)$name


plot(g, layout=layout.fruchterman.reingold,
     vertex.size        = 4,          # Smaller nodes
     vertex.label       = V(g)$name,  # Set the labels
     vertex.label.cex   = 0.8,        # Slightly smaller font
     vertex.label.dist  = 0.4,        # Offset the labels
     vertex.label.color = "black")

# This is equivalent to the preceding code
V(g)$size        <- 4
V(g)$label       <- V(g)$name
V(g)$label.cex   <- 0.8
V(g)$label.dist  <- 0.4
V(g)$label.color <- "black"

# Set a property of the entire graph
g$layout <- layout.fruchterman.reingold

plot(g)
    
    
# View the edges
E(g)

# Set some of the labels to "M"
E(g)[c(2,11,19)]$label <- "M"

# Set color of all to grey, and then color a few red
E(g)$color             <- "grey70"
E(g)[c(2,11,19)]$color <- "red"

plot(g)
```
## 13.6.Creating a Heat Map    
```{r,fig.width=7,fig.height=5}
head(presidents)

str(presidents)

pres_rating <- data.frame(
    rating  = as.numeric(presidents),
    year    = as.numeric(floor(time(presidents))),
    quarter = as.numeric(cycle(presidents))
)
head(pres_rating)

# Base plot
p <- ggplot(pres_rating, aes(x=year, y=quarter, fill=rating))

# Using geom_tile()
p + geom_tile()

# Using geom_raster() - looks the same, but a little more efficient
p + geom_raster()
    
p + geom_tile() +
    scale_x_continuous(breaks = seq(1940, 1976, by = 4)) +
    scale_y_reverse() +
    scale_fill_gradient2(midpoint=50, mid="grey70", limits=c(0,100))
    
```

## 13.7.Creating a Three-Dimensional Scatter Plot    
```{r,fig.width=7,fig.height=5}
# You may need to install first, with install.packages("rgl")
library(rgl)
plot3d(mtcars$wt, mtcars$disp, mtcars$mpg, type="s", size=0.75, lit=FALSE)
    
# Function to interleave the elements of two vectors
interleave <- function(v1, v2)  as.vector(rbind(v1,v2))

# Plot the points
plot3d(mtcars$wt, mtcars$disp, mtcars$mpg,
       xlab="Weight", ylab="Displacement", zlab="MPG",
       size=.75, type="s", lit=FALSE)

# Add the segments
segments3d(interleave(mtcars$wt,   mtcars$wt),
           interleave(mtcars$disp, mtcars$disp),
           interleave(mtcars$mpg,  min(mtcars$mpg)),
           alpha=0.4, col="blue")
    
    
# Make plot without axis ticks or labels
plot3d(mtcars$wt, mtcars$disp, mtcars$mpg,
       xlab = "", ylab = "", zlab = "",
       axes = FALSE,
       size=.75, type="s", lit=FALSE)

segments3d(interleave(mtcars$wt,   mtcars$wt),
           interleave(mtcars$disp, mtcars$disp),
           interleave(mtcars$mpg,  min(mtcars$mpg)),
           alpha = 0.4, col = "blue")

# Draw the box.
rgl.bbox(color="grey50",          # grey60 surface and black text
         emission="grey50",       # emission color is grey50
         xlen=0, ylen=0, zlen=0)  # Don't add tick marks

# Set default color of future objects to black
rgl.material(color="black")

# Add axes to specific sides. Possible values are "x--", "x-+", "x+-", and "x++".
axes3d(edges=c("x--", "y+-", "z--"),
       ntick=6,                       # Attempt 6 tick marks on each side
       cex=.75)                       # Smaller font

# Add axis labels. 'line' specifies how far to set the label from the axis.
mtext3d("Weight",       edge="x--", line=2)
mtext3d("Displacement", edge="y+-", line=3)
mtext3d("MPG",          edge="z--", line=3)
```    
## 13.8.Adding a Prediction Surface to a Three-Dimensional Plot  
```{r,fig.width=7,fig.height=5}
# Given a model, predict zvar from xvar and yvar
# Defaults to range of x and y variables, and a 16x16 grid
predictgrid <- function(model, xvar, yvar, zvar, res = 16, type = NULL) {
  # Find the range of the predictor variable. This works for lm and glm
  # and some others, but may require customization for others.
  xrange <- range(model$model[[xvar]])
  yrange <- range(model$model[[yvar]])

  newdata <- expand.grid(x = seq(xrange[1], xrange[2], length.out = res),
                         y = seq(yrange[1], yrange[2], length.out = res))
  names(newdata) <- c(xvar, yvar)
  newdata[[zvar]] <- predict(model, newdata = newdata, type = type)
  newdata
}


# Convert long-style data frame with x, y, and z vars into a list
# with x and y as row/column values, and z as a matrix.
df2mat <- function(p, xvar = NULL, yvar = NULL, zvar = NULL) {
  if (is.null(xvar)) xvar <- names(p)[1]
  if (is.null(yvar)) yvar <- names(p)[2]
  if (is.null(zvar)) zvar <- names(p)[3]

  x <- unique(p[[xvar]])
  y <- unique(p[[yvar]])
  z <- matrix(p[[zvar]], nrow = length(y), ncol = length(x))

  m <- list(x, y, z)
  names(m) <- c(xvar, yvar, zvar)
  m
}

# Function to interleave the elements of two vectors
interleave <- function(v1, v2)  as.vector(rbind(v1,v2))
    
    
#install.packages("rgl")
library(rgl)

# Make a copy of the data set
m <- mtcars

# Generate a linear model
mod <- lm(mpg ~ wt + disp + wt:disp, data = m)

# Get predicted values of mpg from wt and disp
m$pred_mpg <- predict(mod)

# Get predicted mpg from a grid of wt and disp
mpgrid_df <- predictgrid(mod, "wt", "disp", "mpg")
mpgrid_list <- df2mat(mpgrid_df)

# Make the plot with the data points
plot3d(m$wt, m$disp, m$mpg, type="s", size=0.5, lit=FALSE)

# Add the corresponding predicted points (smaller)
spheres3d(m$wt, m$disp, m$pred_mpg, alpha=0.4, type="s", size=0.5, lit=FALSE)

# Add line segments showing the error
segments3d(interleave(m$wt,   m$wt),
           interleave(m$disp, m$disp),
           interleave(m$mpg,  m$pred_mpg),
           alpha=0.4, col="red")

# Add the mesh of predicted values
surface3d(mpgrid_list$wt, mpgrid_list$disp, mpgrid_list$mpg,
          alpha=0.4, front="lines", back="lines")
    
    
plot3d(mtcars$wt, mtcars$disp, mtcars$mpg,
       xlab = "", ylab = "", zlab = "",
       axes = FALSE,
       size=.5, type="s", lit=FALSE)

# Add the corresponding predicted points (smaller)
spheres3d(m$wt, m$disp, m$pred_mpg, alpha=0.4, type="s", size=0.5, lit=FALSE)

# Add line segments showing the error
segments3d(interleave(m$wt,   m$wt),
           interleave(m$disp, m$disp),
           interleave(m$mpg,  m$pred_mpg),
           alpha=0.4, col="red")

# Add the mesh of predicted values
surface3d(mpgrid_list$wt, mpgrid_list$disp, mpgrid_list$mpg,
          alpha=0.4, front="lines", back="lines")

# Draw the box
rgl.bbox(color="grey50",          # grey60 surface and black text
         emission="grey50",       # emission color is grey50
         xlen=0, ylen=0, zlen=0)  # Don't add tick marks

# Set default color of future objects to black
rgl.material(color="black")

# Add axes to specific sides. Possible values are "x--", "x-+", "x+-", and "x++".
axes3d(edges=c("x--", "y+-", "z--"),
       ntick=6,                       # Attempt 6 tick marks on each side
       cex=.75)                       # Smaller font

# Add axis labels. 'line' specifies how far to set the label from the axis.
mtext3d("Weight",       edge="x--", line=2)
mtext3d("Displacement", edge="y+-", line=3)
mtext3d("MPG",          edge="z--", line=3)
```    
## 13.9.Saving a Three-Dimensional Plot  
```{r,fig.width=7,fig.height=5}
library(rgl)
plot3d(mtcars$wt, mtcars$disp, mtcars$mpg, type="s", size=0.75, lit=FALSE)

rgl.snapshot('3dplot.png', fmt='png')
    
    
rgl.postscript('figs/miscgraph/3dplot.pdf', fmt='pdf')

rgl.postscript('figs/miscgraph/3dplot.ps', fmt='ps')
    
    
# Save the current viewpoint
view <- par3d("userMatrix")

# Restore the saved viewpoint
par3d(userMatrix = view)
    
    
dput(view)

structure(c(0.907931625843048, 0.267511069774628, -0.322642296552658,
0, -0.410978674888611, 0.417272746562958, -0.810543060302734,
0, -0.0821993798017502, 0.868516683578491, 0.488796472549438,
0, 0, 0, 0, 1), .Dim = c(4L, 4L))

    
    
view <- structure(c(0.907931625843048, 0.267511069774628, -0.322642296552658,
0, -0.410978674888611, 0.417272746562958, -0.810543060302734,
0, -0.0821993798017502, 0.868516683578491, 0.488796472549438,
0, 0, 0, 0, 1), .Dim = c(4L, 4L))

par3d(userMatrix = view)
```    
## 13.10.Animating a Three-Dimensional Plot    
```{r,fig.width=7,fig.height=5}
library(rgl)
plot3d(mtcars$wt, mtcars$disp, mtcars$mpg, type="s", size=0.75, lit=FALSE)

play3d(spin3d())
    
# Spin on x-axis, at 4 rpm, for 20 seconds
play3d(spin3d(axis=c(1,0,0), rpm=4), duration=20)
    
# Spin on z axis, at 4 rpm, for 15 seconds
movie3d(spin3d(axis=c(0,0,1), rpm=4), duration=15, fps=50)
```
## 13.11.Creating a Dendrogram
```{r,fig.width=7,fig.height=5}
library(gcookbook) # For the data set

# Get data from year 2009
c2 <- subset(countries, Year==2009)

# Drop rows that have any NA values
c2 <- c2[complete.cases(c2), ]

# Pick out a random 25 countries
# (Set random seed to make this repeatable)
set.seed(201)
c2 <- c2[sample(1:nrow(c2), 25), ]

c2

rownames(c2) <- c2$Name
c2 <- c2[,4:7]
c2

c3 <- scale(c2)
c3

attr(,"scaled:scale")

hc <- hclust(dist(c3))

# Make the dendrogram
plot(hc)

# With text aligned
plot(hc, hang = -1)
```
## 13.12.Creating a Vector Field
```{r,fig.width=7,fig.height=5}
library(gcookbook) # For the data set
head(isabel)

islice <- subset(isabel, z == min(z))

ggplot(islice, aes(x=x, y=y)) +
       geom_segment(aes(xend = x + vx/50, yend = y + vy/50),
                    size = 0.25)   # Make the line segments 0.25 mm thick
    
    
#====================================
# Take a slice where z is equal to the minimum value of z
islice <- subset(isabel, z == min(z))

# Keep 1 out of every 'by' values in vector x
every_n <- function(x, by = 2) {
    x <- sort(x)
    x[seq(1, length(x), by = by)]
}

# Keep 1 of every 4 values in x and y
keepx <- every_n(unique(isabel$x), by=4)
keepy <- every_n(unique(isabel$y), by=4)

# Keep only those rows where x value is in keepx and y value is in keepy
islicesub <- subset(islice, x %in% keepx  &  y %in% keepy)
    
    
# Need to load grid for arrow() function
library(grid)

# Make the plot with the subset, and use an arrowhead 0.1 cm long
ggplot(islicesub, aes(x=x, y=y)) +
    geom_segment(aes(xend = x+vx/50, yend = y+vy/50),
                 arrow = arrow(length = unit(0.1, "cm")), size = 0.25)
    
    
# The existing 'speed' column includes the z component. We'll calculate
# speedxy, the horizontal speed.
islicesub$speedxy <- sqrt(islicesub$vx^2 + islicesub$vy^2)

# Map speed to alpha
ggplot(islicesub, aes(x=x, y=y)) +
    geom_segment(aes(xend = x+vx/50, yend = y+vy/50, alpha = speed),
                 arrow = arrow(length = unit(0.1,"cm")), size = 0.6)
    
    
# Get USA map data
usa <- map_data("usa")

# Map speed to colour, and set go from "grey80" to "darkred"
ggplot(islicesub, aes(x=x, y=y)) +
    geom_segment(aes(xend = x+vx/50, yend = y+vy/50, colour = speed),
                 arrow = arrow(length = unit(0.1,"cm")), size = 0.6) +
    scale_colour_continuous(low="grey80", high="darkred") +
    geom_path(aes(x=long, y=lat, group=group), data=usa) +
    coord_cartesian(xlim = range(islicesub$x), ylim = range(islicesub$y))
    
    
# Keep 1 out of every 5 values in x and y, and 1 in 2 values in z
keepx <- every_n(unique(isabel$x), by=5)
keepy <- every_n(unique(isabel$y), by=5)
keepz <- every_n(unique(isabel$z), by=2)

isub <- subset(isabel, x %in% keepx  &  y %in% keepy  &  z %in% keepz)

ggplot(isub, aes(x=x, y=y)) +
    geom_segment(aes(xend = x+vx/50, yend = y+vy/50, colour = speed),
                 arrow = arrow(length = unit(0.1,"cm")), size = 0.5) +
    scale_colour_continuous(low="grey80", high="darkred") +
    facet_wrap( ~ z)
```    
## 13.13.Creating a QQ Plot  
```{r,fig.width=7,fig.height=5}
library(gcookbook) # For the data set

# QQ plot of height
qqnorm(heightweight$heightIn)
qqline(heightweight$heightIn)

# QQ plot of age
qqnorm(heightweight$ageYear)
qqline(heightweight$ageYear)
```    
## 13.14.Creating a Graph of an Empirical Cumulative Distribution Function  
```{r,fig.width=7,fig.height=5}
library(gcookbook) # For the data set

# ecdf of heightIn
ggplot(heightweight, aes(x=heightIn)) + stat_ecdf()

# ecdf of ageYear
ggplot(heightweight, aes(x=ageYear)) + stat_ecdf()
```    
## 13.15.Creating a Mosaic Plot  
```{r,fig.width=7,fig.height=5}
UCBAdmissions

# Print a "flat" contingency table
ftable(UCBAdmissions)

dimnames(UCBAdmissions)

# You may need to install first, with install.packages("vcd")
library(vcd)
# Split by Admit, then Gender, then Dept
mosaic( ~ Admit + Gender + Dept, data=UCBAdmissions)
    
    
mosaic( ~ Dept + Gender + Admit, data=UCBAdmissions,
    highlighting="Admit", highlighting_fill=c("lightblue", "pink"),
    direction=c("v","h","v"))
    
    
# Another possible set of splitting directions
mosaic( ~ Dept + Gender + Admit, data=UCBAdmissions,
    highlighting="Admit", highlighting_fill=c("lightblue", "pink"),
    direction=c("v", "v", "h"))

# This order makes it difficult to compare male and female
mosaic( ~ Dept + Gender + Admit, data=UCBAdmissions,
    highlighting="Admit", highlighting_fill=c("lightblue", "pink"),
    direction=c("v", "h", "h"))
```    
## 13.16.Creating a Pie Chart  
```{r,fig.width=7,fig.height=5}
library(MASS)  # For the data set

# Get a table of how many cases are in each level of fold
fold <- table(survey$Fold)
fold

# Make the pie chart
pie(fold)

pie(c(99, 18, 120), labels=c("L on R", "Neither", "R on L"))
```    
## 13.17.Creating a Map  
```{r,fig.width=7,fig.height=5}
library(maps) # For map data
# Get map data for USA
states_map <- map_data("state")

ggplot(states_map, aes(x=long, y=lat, group=group)) +
    geom_polygon(fill="white", colour="black")

# geom_path (no fill) and Mercator projection
ggplot(states_map, aes(x=long, y=lat, group=group)) +
    geom_path() + coord_map("mercator")
    
# Get map data for world
world_map <- map_data("world")
head(world_map)

head(sort(unique(world_map$region)))

# You might have noticed that it's a little out of date!
    
east_asia <- map_data("world", region=c("Japan", "China", "North Korea",
                                        "South Korea"))
# Map region to fill color
ggplot(east_asia, aes(x=long, y=lat, group=group, fill=region)) +
    geom_polygon(colour="black") +
    scale_fill_brewer(palette="Set2")
    
    
# Get New Zealand data from world map
nz1 <- map_data("world", region="New Zealand")
nz1 <- subset(nz1, long > 0 & lat > -48)        # Trim off islands
ggplot(nz1, aes(x=long, y=lat, group=group)) + geom_path()

# Get New Zealand data from the nz map
nz2 <- map_data("nz")
ggplot(nz2, aes(x=long, y=lat, group=group)) + geom_path()
```    
## 13.18.Creating a Choropleth Map  
```{r,fig.width=7,fig.height=5}
# Transform the USArrests data set to the correct format
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
head(crimes)

#install.packages("maps")
library(maps) # For map data
states_map <- map_data("state")

# Merge the data sets together
crime_map <- merge(states_map, crimes, by.x="region", by.y="state")

# After merging, the order has changed, which would lead to polygons drawn in
# the incorrect order. So, we sort the data.
head(crime_map)


library(plyr)  # For arrange() function
# Sort by group, then order
crime_map <- arrange(crime_map, group, order)
head(crime_map)

ggplot(crime_map, aes(x=long, y=lat, group=group, fill=Assault)) +
    geom_polygon(colour="black") +
    coord_map("polyconic")
    
    
ggplot(crimes, aes(map_id = state, fill=Assault)) +
    geom_map(map = states_map, colour="black") +
    scale_fill_gradient2(low="#559999", mid="grey90", high="#BB650B",
                         midpoint=median(crimes$Assault)) +
    expand_limits(x = states_map$long, y = states_map$lat) +
    coord_map("polyconic")
    
    
# Find the quantile bounds
qa <- quantile(crimes$Assault, c(0, 0.2, 0.4, 0.6, 0.8, 1.0))
qa

# Add a column of the quantile category
crimes$Assault_q <- cut(crimes$Assault, qa,
                      labels=c("0-20%", "20-40%", "40-60%", "60-80%", "80-100%"),
                      include.lowest=TRUE)
head(crimes)

# Generate a discrete color palette with 5 values
pal <- colorRampPalette(c("#559999", "grey80", "#BB650B"))(5)
pal

ggplot(crimes, aes(map_id = state, fill=Assault_q)) +
    geom_map(map = states_map, colour="black") +
    scale_fill_manual(values=pal) +
    expand_limits(x = states_map$long, y = states_map$lat) +
    coord_map("polyconic") +
    labs(fill="Assault Rate\nPercentile")

    
    
# The 'state' column in the crimes data is to be matched to the 'region' column
# in the states_map data
ggplot(crimes, aes(map_id = state, fill=Assault)) +
    geom_map(map = states_map) +
    expand_limits(x = states_map$long, y = states_map$lat) +
    coord_map("polyconic")
```    
## 13.19.Making a Map with a Clean Background  
```{r,fig.width=7,fig.height=5}
# Create a theme with many of the background elements removed
theme_clean <- function(base_size = 12) {
require(grid) # Needed for unit() function
  theme_grey(base_size) %+replace%
  theme(
    axis.title        = element_blank(),
    axis.text         = element_blank(),
    panel.background  = element_blank(),
    panel.grid        = element_blank(),
    axis.ticks.length = unit(0, "cm"),
    axis.ticks.margin = unit(0, "cm"),
    panel.margin      = unit(0, "lines"),
    plot.margin       = unit(c(0, 0, 0, 0), "lines"),
    complete = TRUE
  )
}
    
ggplot(crimes, aes(map_id = state, fill=Assault_q)) +
    geom_map(map = states_map, colour="black") +
    scale_fill_manual(values=pal) +
    expand_limits(x = states_map$long, y = states_map$lat) +
    coord_map("polyconic") +
    labs(fill="Assault Rate\nPercentile") +
    theme_clean()
```    
## 13.20.Creating a Map from a Shapefile  
```{r,fig.width=7,fig.height=5}
#install.packages("maptools")
#install.packages("sp")
# 首先要安装这两个包
library(maptools)
gpclibPermit()

# 地图包从这里下载：http://www.gadm.org/
# 记住要把几个TWN_adm2的文件都放在TWN_adm文件夹下
# 仅仅放一个shp会报错
# Load the shapefile and convert to a data frame
taiwan_shp <- readShapePoly("TWN_adm/TWN_adm2.shp")
taiwan_map <- fortify(taiwan_shp)

ggplot(taiwan_map, aes(x = long, y = lat, group=group)) + geom_path()
    
    
taiwan_shp <- readShapePoly("TWN_adm/TWN_adm2.shp")

# Look at the structure of the object
head(str(taiwan_shp))

taiwan_map <- fortify(taiwan_shp)
head(taiwan_map)

# Send the SpatialPolygonsDataFrame directly to ggplot()
ggplot(taiwan_shp, aes(x=long, y=lat, group=group)) + geom_path()
```
